Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-09 sattose/paper.tex
Fixed this text a bit

\subsection{Type 1R clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Therefore, we propose an alternative definition of type 1 clones. We have named this type 1R clones, indicate that this definition is separate from type 1 clones in literature. The ``R'' stands for refactoring, to indicate that this is type is refactoring oriented (and may be less suitable for, for instance, large scale clone analysis). Type 1R clones differ from type 1 clones by the folowing aspects:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
  \item \textbf{Compare the equality of the fully qualified indentifier for method references and call signatures.}
\end{itemize}

@@

As indicated in section \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test. As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to all Maven projects. As no pom.xml files are included in the corpus, we cloned the lastest version of each project in the corpus. We then removed each project that contained no ``pom.xml'' file (a file that describes the dependencies used by the project). We then filtered the corpus further to make sure each project contained a ``src/main/java'' folder, to be sure no test files or other redundant sources are included in the clone detection. As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the ``pom.xml'' file).

>>>>

\subsection{Type 1R clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Therefore, we propose an alternative definition of type 1 clones. We have named this it ``type 1R clones'', to indicate that this definition is separate from type 1 clones in literature. The ``R'' stands for refactoring, to indicate that this is type is refactoring oriented (and may be less suitable for, for instance, large scale clone analysis). Type 1R clones differ from type 1 clones by the following aspects:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
  \item \textbf{Compare the equality of the fully qualified indentifier for method references and call signatures.}
\end{itemize}

@@

As indicated in section \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test. As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects. Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies. As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus. We then removed each project that contained no ``pom.xml'' file (a file that describes the dependencies used by the project). We then filtered the corpus further to make sure each project contained a ``src/main/java'' folder, to be sure no test files or other redundant sources are included in the clone detection. As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the ``pom.xml'' file).
